---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CountNAByGroup

<!-- badges: start -->
<!-- badges: end -->

The goal of CountNAByGroup is to create a function to count missing values for all columns in the dataset by group. The name of the function is `count_all_missing_by_group()`

Given a data frame `data` and a column `group`, `count_all_missing_by_group()` creates a new data frame with one row per level of `group`. The first column of the output data frame contains the levels of `group`, and the rest of the columns contain the number of missing values for all columns in `data` except `group`.


## Installation

You can install the development version of CountNAByGroup from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/CountNAByGroup")
```

## Example

This example computes the number of missing values in the `airquality` dataset grouped by the `Month` column. 

```{r example 1}
library(CountNAByGroup) # load our package
library(datasets) # load the library containing airquality data
count_all_missing_by_group(airquality, Month)
```


This example has the same output as the last example, but shows off an alternative way of invoking the `count_all_missing_by_group()`: piping the dataset into the function. 

```{r example 2}
airquality |> count_all_missing_by_group(Month) 
```
